MixEth: efficient, trustless coin mixing service for Ethereum

### 2019-04-08 article/OASIcs/MixEth_Seres_Nagy_Buckland_Burcsi_2019.tex
OASIcs version of paper added

\documentclass[a4paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{authblk}
\usepackage{booktabs}
\usepackage{ae,aecompl}
%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{pgfplots}
\pgfplotsset{compat=1.12}
\usepackage[group-separator={,}]{siunitx}
\usepackage{amsmath}
\usepackage{wrapfig}
\usepackage{amsthm}
\usetikzlibrary{arrows,automata}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{breqn}
\usepackage{algpseudocode}
\usepackage{float}
\usepackage{tikz}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\usepackage{eufrak}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage[toc,page]{appendix}
\usepackage{color}
\definecolor{lightgray}{rgb}{.9,.9,.9}
\definecolor{darkgray}{rgb}{.4,.4,.4}
\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
\floatname{algorithm}{Procedure}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

@@

\usepackage{graphicx}
\usepackage[
n,
operators,
advantage,
sets,
adversary,
landau,
probability,
notions,	
logic,
ff,
mm,
primitives,
events,
complexity,
asymptotics,
keys]{cryptocode}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

@@

\title{MixEth: efficient, trustless coin mixing service for Ethereum}
\author[1]{István András Seres}
\author[1]{Dániel A. Nagy}
\author[2]{Chris Buckland}
\author[1]{Péter Burcsi}
\affil[1]{Department of Computer Algebra, Eötvös Loránd University}
\affil[2]{King's College London}
\begin{document}
\maketitle

\begin{abstract}
Coin mixing is a prevalent privacy-enhancing technology for cryptocurrency users. In this paper, we present MixEth, which is a trustless coin mixing service for Turing-complete blockchains. MixEth does not rely on a trusted setup and is more efficient than any proposed trustless coin tumbler. It requires only 3 on-chain transactions at most per user and 1 off-chain message. It achieves strong notions of anonymity and is able to resist denial-of-service attacks. Furthermore the underlying protocol can also be used to efficiently shuffle ballots, ciphertexts in a trustless and decentralized manner.     
\end{abstract}
\keywords{Cryptography, Verifiable shuffle, Anonymity, Cryptocurrency, Ethereum, Coin mixer, State Channel}

@@

\subsection{ECDSA with arbitrary generator element}
Elliptic Curve Digital Signature Algorithm (ECDSA) is a key component of MixEth. ECDSA is widely deployed in practice, where in most cases signatures are generated and verified with respect to a fixed generator element of the underlying group \cite{fersch2016provable}. Since all generators are equal from a security point of view, a single generator element is usually fixed in order to promote standardization and assists usability.

@@

\subsection{Security goals} \label{securitygoals}
We are aiming to achieve and prove the same notions of security as the ones defined in \cite{meiklejohn2018mobius}, namely anonymity, availability and theft prevention. These notions of anonymity, availability and theft prevention were introduced in \cite{meiklejohn2018mobius}, which are included in this section for sake of self-containedness.

@@

From now on, we will denote a specific key in a given session as as $tumbler.keys_{B}$.

@@

\begin{definition}
	Define $\textbf{Adv}^{d-anon}_{mix,\adv}(\lambda) = 2\Pr[\textsf{G}^{d-anon}_{mix,\adv}(\lambda)]-1\ for\ d \in \{dep, with\}$, where these games are defined as follows:

	\begin{table}[H]
		\centering
		\begin{tabular}{cc}    
			\begin{minipage}{7cm}
					\procedure{MAIN $\textsf{G}^{dep-anon}_{mix,\adv}(\lambda)$}{%
						(pk_{i},sk_{i})\stackrel{\$}{\leftarrow}\kgen(1^{\lambda}) \ \forall i \in [n]\\
						\textsf{PK}_A\leftarrow\{pk_i\}^{n}_{i=1};C,H_{d}, tumblers \leftarrow \emptyset\\
						b \stackrel{\$}{\leftarrow} \bin \\
						(state,j,pk, i_{0},i_{1}) \stackrel{\$}{\leftarrow} \adv^{CORR,AD,HD,AW} (1^\lambda, \textsf{PK}_{A}) \\
						tx \stackrel{\$}{\leftarrow} Deposit(tumblers[j], sk_{A_{{l}_{b}}}, pk) \\
						b^{’}\stackrel{\$}{\leftarrow} \adv^{CORR,AD,HD,AW}(state, tx) \\
						\pcreturn b = b^{’} }
			\end{minipage}
			&
			\begin{minipage}{7cm}
				\procedure{MAIN $\textsf{G}^{with-anon}_{mix,\adv}(\lambda)$}{%
					(pk_{i},sk_{i})\stackrel{\$}{\leftarrow}\kgen(1^{\lambda}) \ \forall i \in [n]\\
					\textsf{PK}_B\leftarrow\{pk_i\}^{n}_{i=1};C,H_{d}, tumblers \leftarrow \emptyset\\
					b \stackrel{\$}{\leftarrow} \bin \\
					(state,j,pk, l_{0},l_{1}) \stackrel{\$}{\leftarrow} \adv^{CORR,AD,HD,AW} (1^\lambda, \textsf{PK}_{B}) \\
					\textsf{PK}\leftarrow tumblers[j].keys_{B}\\
					if(pk_{B_{l_{0}}}\notin \textsf{PK})\lor(pk_{B_{l_{1}}}\notin \textsf{PK})\ return\ 0\\
					tx \stackrel{\$}{\leftarrow} Withdraw(tumblers[j], sk_{B_{{l}_{b}}}) \\
					b^{’}\stackrel{\$}{\leftarrow} \adv^{CORR,AD,HD,AW}(state, tx) \\
					if(pk_{l_{b}}\in C \ for\ b \in \bin)\ return\ 0 \\
					if((j,l_{b},\cdot))\in H_{w} \ for\ b \in \bin)\ return\ 0\\
					\pcreturn b = b^{’} }		
			\end{minipage}
		\end{tabular}
	\end{table}	
Then the tumbler satisfies sender or recipient anonymity if for all PPT adversaries $\adv$ there exists a negligible function $\nu(\cdot)$ such that $\textbf{Adv}^{dep-anon}_{mix,\adv}(\lambda) < \nu(\lambda)$ or $\textbf{Adv}^{with-anon}_{mix,\adv}(\lambda) < \nu(\lambda)$ respectively.	
\end{definition}

@@

\begin{definition}
	Define $\textbf{Adv}^{avail}_{mix,\adv}(\lambda) = \Pr[\textsf{G}^{avail}_{mix,\adv}(\lambda)]$, where the game is defined as follows:

	\begin{table}[H]
		\centering
		\begin{tabular}{c}    
			\begin{minipage}{7cm}
				\procedure{MAIN $\textsf{G}^{avail}_{mix,\adv}(\lambda)$}{%
					(pk_{i},sk_{i})\stackrel{\$}{\leftarrow}\kgen(1^{\lambda}) \ \forall i \in [n]\\
					\textsf{PK}_B\leftarrow\{pk_i\}^{n}_{i=1};C,H_{w} \leftarrow \emptyset\\
					(l,j)\stackrel{\$}{\leftarrow} \adv^{CORR,AD,HW,AW}(1^{\lambda},\textsf{PK}_{B}) \\
					b \leftarrow  \textsf{VerifyWithdraw}(\textsf{tumblers}[j], \textsf{Withdraw}(sk_{l})) \\
					if ((pk_{l}\in C)\ \lor\ ((j,l,\cdot)\in H_{w}))\ return \ 0 \\
					\pcreturn (b=0)\land(pk_{l}\in tumblers[j].keys_{B})}
			\end{minipage}
		\end{tabular}
	\end{table}	
	Then the tumbler satisfies availability if for all PPT adversaries $\adv$ there exists a negligible function $\nu(\cdot)$ such that $\textbf{Adv}^{avail}_{mix,\adv}(\lambda) < \nu(\lambda)$.
\end{definition}

\subsubsection{Theft prevention} \label{sec:theftprevention}
We would like to ensure that neither coins can be withdrawn twice, nor withdrawn by anyone other but the intended recipient. Theft prevention is defined formally as follows:

\begin{definition}
	Define $\textbf{Adv}^{theft}_{mix,\adv}(\lambda) = \Pr[\textsf{G}^{theft}_{mix,\adv}(\lambda)]$, where the game is defined as follows:

@@

\subsection{MixEth formal specification}

\begin{table}[H]
	\centering
	\begin{tabular}{cccc}    
		\begin{minipage}{5.5cm}
			\procedure{\textsf{Deposit}($sk_A, pk_{B}$)}{%
				\pcreturn \textsf{FormTx}(sk_A,id_{\textsf{contract}}, amt, pk_{B}) }
		\end{minipage}
		&
		\begin{minipage}{5.4cm}
			\procedure{\textsf{VerifyDeposit}(tx)}{%
				if\ (tx[amt] \neq id_{\textsf{contract}}[amt]) \ return\ 0 \\
				if\ (pk_{B} \notin \mathbb{G}) \ return\ 0 \\
				\pcreturn \textsf{VerifyTx(tx)}  }
		\end{minipage}
		&
		\begin{minipage}{4cm}
			\procedure{\textsf{ProcessDeposit(tx)}}{%
				add\ \textsf{addr(tx[pk]) to initPubKeys[]}}
		\end{minipage}
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\begin{tabular}{cccc}    
		\begin{minipage}{5cm}
			\procedure{\textsf{Shuffle($PK,C^{*}$)}}{%
				c\stackrel{\$}{\leftarrow}\mathbb{Z}_{|\mathbb{G}|} \\
				C^{'*} \leftarrow cC^{*} \\
				PK^{'} = \{pk^{'}_{i}|pk^{'}_{i}=c*pk_{i} \forall i \in [1..n]\} \\
				\pcreturn (PK^{'},C^{'*}) }
		\end{minipage}
		&
		\begin{minipage}{5.7cm}
			\procedure{\textsf{UploadShuffle($sk_{A},PK,C^{*}$)}}{%
				\pcreturn \textsf{FormTx}(sk_{A},id_{contract},(PK,C^{*})) }
		\end{minipage}
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\begin{tabular}{ccc}
		\begin{minipage}{6.3cm}
			\procedure{\textsf{Challenge}($proof_{ChP}(C^{*},sC^{*},C^{'*},sC^{'*}),PK, PK^{'}$)}{%
				if\ (\lnot Verify(proof_{ChP}) ) \ return\ 0 \\
				if\ (sC^{*} \notin PK) \ return\ 0 \\
				delete (C^{'},PK^{'})\\
				slashDeposit(shuffler(C^{'},PK^{'}))\\
				\pcreturn 1  }
		\end{minipage}
		&
		\begin{minipage}{4.6cm}
			\procedure{\textsf{WithdrawShufflingDeposit($sk_{A}$)}}{%
				\pcreturn \textsf{FormTx($sk_{A}, id_{contract},0$)} }
		\end{minipage}
		&
		\begin{minipage}{4.6cm}
			\procedure{\textsf{VerifyWithdrawShufflingDeposit($pk_{A}$)}}{%
				\pcreturn shufflingDepositSlashed(pk_{A}) }
		\end{minipage}
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\begin{tabular}{cccc}    
		\begin{minipage}{4.7cm}
			\procedure{\textsf{Withdraw($s,C^{*}$)}}{%
				\sigma \leftarrow \sig(C^{*},s, sC^{*}||msg.sender) \\
				\pcreturn \textsf{FormTx($s,C^{*}, id_{\textsf{contract}, 0}, \sigma$)} }
		\end{minipage}
		&
		\begin{minipage}{6.3cm}
			\procedure{\textsf{VerifyWithdraw(tx)}}{%
				if\ (sC^{*} \notin id_{\textsf{contract}}[lastShuffle] ) \ return\ 0 \\
				if\ (\lnot\verify(C^{*}, sC^{*},\sigma, sC^{*}||tx.sender)) \ return\ 0 \\
				\pcreturn \textsf{VerifyTx(tx)}  }
		\end{minipage}
		&
		\begin{minipage}{4cm}
			\procedure{\textsf{ProcessWithdraw(tx)})}{%
				delete\ sC^{*} from\ id_{\textsf{contract}}[lastShuffle]   \\
				tx^{'}\stackrel{\$}{\leftarrow} \textsf{FormTx}(id_{contract}, tx.sender, amt) }
		\end{minipage}
	\end{tabular}
\end{table}

\section{Security}
This section provides informal ideas to the security proofs for the notions of security introduced in Section \ref{securitygoals}. Formal reductions are enclosed in the Appendices.

\subsection{Recipient anonymity}
The withdrawing transaction for recipient $B$ sends funds to the public key $s_{B}C^{*}$. This public key does not reveal any links to the original $s_{B}G$ in case if at least one honest sender shuffled and the DDH assumption holds. Adversary can only distinguish between honest recipients public keys with negligible probability. See reduction proof in Appendix \ref*{appendanon}.
\subsection{Availability}
If an adversary is able to destroy an honest recipient's funds' availability, it implies that adversary $\adv$ either breaks the completeness of the Chaum-Pedersen protocol or successfully launched an eclipse attack against the honest recipient, who cannot send any transactions to honest Ethereum peers.
\subsection{Theft prevention} 
If an adversary is able to steal funds from other users than it would imply that they managed to create a valid message/signature, $(m,\sigma)$ pair for the final shuffled public key of an honest recipient without having access to the secret key of the honest recipient. This contradicts to the assumption that ECDSA is existentially unforgeable. Reduction proof is enclosed in Appendix \ref*{appendtheft}. 
\begin{table}[H] 
	\caption{Security properties achieved by each coin mixing protocol.}
	\centering 
	\begin{tabular}{@{\extracolsep{6pt}}lcccccc@{}}

		\toprule
		\hline
		&\multicolumn{3}{c}{Anonimity against}& \multicolumn{2}{c}{Availability}&Theft prevention\\
		\cline{2-4}\cline{5-6}&outsiders&senders&recipients&sender&tumbler\\
		\hline
		\midrule
		\textbf{Centralized} & & \\
		\midrule
		Mixcoin \cite{bonneau2014mixcoin} & TTP       & \xmark  &\cmark&\cmark&\xmark&TTP      \\
		Blindcoin \cite{valenta2015blindcoin} & \cmark &\xmark&\cmark&\cmark&\xmark&TTP        \\
		TumbleBit \cite{heilman2017tumblebit} & \cmark &\cmark&\cmark&\cmark&\xmark&\cmark       \\
		\midrule
		\textbf{Decentralized}      &    &      \\
		\midrule
		Coinjoin \cite{maxwell2013coinjoin} & \cmark   &\xmark&\cmark&\xmark&n.a.&\cmark       \\
		Coinshuffle \cite{ruffing2014coinshuffle} & \cmark&\xmark&\cmark&\xmark&n.a.&\cmark       \\
		XIM \cite{bissias2014sybil} & \cmark      &\xmark&\cmark&\cmark&n.a.&\cmark       \\
		Möbius \cite{meiklejohn2018mobius}     &\cmark&\cmark&\xmark&\cmark&\cmark&\xmark        \\
		Miximus \cite{miximus2018}&\cmark&\xmark&\xmark&\cmark&\cmark&\cmark  \\
		MixEth&\cmark&\cmark&\xmark&\cmark&\cmark&\cmark  \\
		\bottomrule
	\end{tabular}
	\label{table:securityproperties}
\end{table}

@@

\begin{wrapfigure}{r}{0.7\textwidth}
	\centering
	\includegraphics[scale=0.7]{./withdrawalComplexity.jpg}
	\captionsetup{justification=centering}
	\caption{Gas complexity of withdraw transactions for various trustless Ethereum coin mixers}
\end{wrapfigure}

@@

All MixEth smart contracts were written in the Solidity language, which is currently the dominant language for developing Ethereum smart contracts. MixEth contracts are compiled using the latest version of the Solidity compiler in order to take advantage of the latest language features such as the possibility to return dynamic-sized arrays from contract functions. Note that these implementations are only proof-of-concept implementations, expect further improvements. All MixEth contracts are available online\footnote{https://github.com/seresistvanandras/MixEth}.

\subsection{Fully on-chain implementation} \label{fullyonchainimpl}

\begin{wrapfigure}{r}{0.3\textwidth}
	\centering
\begin{tikzpicture}[shorten >=1pt,node distance=3cm,on grid,auto] 
\node[state,initial above,initial text=] (q_deposit) {$q_{deposit_{i}}$}; 
\node[state] (q_shuffle) [below=of q_deposit ] {$q_{shuffle_{j}}$};
\node[state] (q_challenge) [below=of q_shuffle ] {$q_{challenge}$};
\node[state, accepting below, below=of q_challenge] (q_withdraw) {$q_{withdraw_{k}}$};
\path[->]
(q_deposit) edge [loop right] node {$i+1$} ()
(q_deposit) edge node {$i=N$} (q_shuffle)		
(q_shuffle) edge node {} (q_challenge)
(q_challenge) edge [bend right, swap] node {$noFraud, j+1$} (q_shuffle)
(q_challenge) edge [bend left] node {$fraud, j-1$} (q_shuffle)
(q_challenge) edge node {$j=N^{'}$} (q_withdraw)
(q_withdraw) edge [loop right] node {$k+1$} ();
\end{tikzpicture}
\captionsetup{justification=centering}
\caption{Shuffle-and-challenge paradigm implemented for the fully on-chain version of MixEth}
\label{fig:shuffleandchallenge}
\end{wrapfigure}

Conceivably mixers would like to minimize off-chain coordination, therefore in our first implementation of the MixEth protocol, we assumed that all transactions will take place on-chain. There is only a single off-chain message from receiver to sender, where receiver delivers their public key to the sender. The rest of the protocol happens entirely on-chain.

On-chain storage is extremely expensive: it requires $\num[group-separator={,}]{20000}$ gas to store a $256$-bit number, however if a particular storage slot is already taken and one wants to overwrite it with a non-zero element then storing only consumes $\num[group-separator={,}]{5000}$ gas. To minimize on-chain storage costs, only the last two list of shuffled public keys are stored in the MixEth contract's permanent storage. Note that storing only the latest list of shuffled public keys would not be enough, since honest receivers could not prove to the contract that their shuffled public key is compromised unless also the last but first list of shuffled keys is also available for the contract to check the Chaum-Pedersen proof against. Such a storage structure implies that after uploading the new list of shuffled public keys, a challenging period should proceed in order to let receivers check the correctness of the shuffle and whether their shuffled public key is stored in the smart contract, see Figure \ref{fig:shuffleandchallenge}. Furthermore we also allow senders to shuffle and deposit new public keys at the same time, meaning that only $3$ on-chain transactions (shuffle, withdraw mixed coins and withdraw shuffling deposit) are sufficient to complete the protocol. We left it as a future work to determine the optimal ratio of mixed coins and shuffling deposits in order to incentivise correct shuffling.

A great advantage of the fully on-chain version of MixEth is that it allows dynamic anonymity sets. One could potentially deposit funds to the contract and shuffle public keys and leave funds in the mixing contract for indefinite amount of time. As soon as the anonymity set is large enough a receiver could withdraw their assets. The whole process is represented as a finite automata as shown in Figure \ref{fig:shuffleandchallenge}. A receiver in a MixEth contract with $N$ senders could withdraw their funds after $N^{'}$ shuffling rounds, where $N^{'}$ is arbitrary.  This dynamic nature of the contract could even lead to a single monolithic MixEth contract instead of having multiple MixEth contracts with significantly fragmented anonymity sets. A single MixEth contract is able to support the mixing of ether and ERC-20 compatible tokens as well. However note that the gas complexity of shuffling transactions grows linearly in the number of participants, therefore the fully on-chain implementation is not capable to support extremely large anonymity sets with participants more than a few hundreds.

Also note that the on-chain cost of a shuffle transaction could be amortized among participants. Specifically if there is a group of senders and/or receivers who trust each other they could collectively charge any of them to shuffle once. Since they trust their peer, all the rest of the group does not need to shuffle anymore. Later non-shufflers could reimburse the only shuffler for their services either on-chain or off-chain.

\begin{wrapfigure}{r}{0.4\textwidth}
	\centering
	\begin{tikzpicture}[shorten >=1pt,node distance=4cm,on grid,auto] 
	\node[state,initial above,initial text=] (q_deposit) {$q_{deposit_{i}}$}; 
	\node[state] (q_shuffle) [below=of q_deposit ] {$q_{shuffle_{j}}$};
	\node[state, below=of q_shuffle] (q_no_fraud) {$q_{noFraud_j}$};	\node[state, accepting, right=of q_no_fraud] (q_fraud) {$q_{fraud}$};
	\node[state, accepting below, below=of q_no_fraud] (q_withdraw) {$q_{withdraw_{k}}$};
	\path[->]
	(q_deposit) edge [loop left] node {$i+1$} ()
	(q_deposit) edge node {$i=N$} (q_shuffle)		
	(q_shuffle) edge [loop left] node {$j+1$} ()
	(q_shuffle) edge node {$j=N$} (q_no_fraud)
	(q_no_fraud) edge node {$j=N$} (q_withdraw)
	(q_no_fraud) edge [loop left] node {$j+1$} ()
	(q_no_fraud) edge node {} (q_fraud)
	(q_withdraw) edge [loop left] node {$k+1$} ();
	\end{tikzpicture}
	\captionsetup{justification=centering}
	\caption{Shuffle-then-challenge paradigm implemented for the channelised version of MixEth}
	\label{fig:shufflethenchallenge}
\end{wrapfigure}

@@

Given these adaptations the application proceeds as follows, all participants including senders, shufflers and receivers, deposit funds in a mutli-signature wallet compatible with the Counterfactual framework, they then follow the installation protocols specified by the framework to install the adapted MixEth logic. Afterwards each participant signs a transaction that transfers an equal amount to each withdrawer from the multi-sig, dependent on correct execution of the channelised MixEth application logic. This application logic proceeds as follows: each sender names a public key of a shuffler as in the deposit stage of the on-chain application, then each shuffler takes it in turn to shuffle. After all shuffles have taken place each withdrawer is given a turn to either declare fraud or no-fraud on any shuffle round. Finally each withdrawer then provides proof of ownership by submitting a valid signature on the modified ECDSA scheme. If any of these steps does not occur, or does not occur correctly, the protocol aborts and the conditional transfer does not occur. In this case the perpetrator loses a deposit, either through fraud proof or through failure to take their turn when state is published on-chain. A further modification would be to distribute the slashed deposit to each of the other participants, compensating them for their lost time and the gas costs associated with proving the fault of the other party. Following this protocol the on-chain transactions are now reduced to: one transaction from each participant to deposit funds into the multi-sig, and a set of transactions that send funds from the multi-sig to each of the withdrawers and deposits back to each of the other participants. The modified procedure of the MixEth protocol is illustrated as a finite automate in Figure \ref{fig:shufflethenchallenge}. Note that all three $N$s are the same. In a channelised MixEth contract there are exactly $N$ depositors, $N$ shufflers and $N$ receivers.

@@

>>>>

\documentclass[a4paper,UKenglish,cleveref, autoref]{oasics-v2019}
%This is a template for producing OASIcs articles. 
%See oasics-manual.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
%for section-numbered lemmas etc., use "numberwithinsect"
%for enabling cleveref support, use "cleveref"
%for enabling cleveref support, use "autoref"

\usepackage{booktabs}
%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory
\usepackage{pgfplots}
\pgfplotsset{compat=1.12}
\usepackage[group-separator={,}]{siunitx}
\usepackage{amsmath}
\usepackage{wrapfig}
\usepackage{amsthm}
\usetikzlibrary{arrows,automata}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{breqn}
\usepackage{algpseudocode}
\usepackage{float}
\usepackage{tikz}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\usepackage{eufrak}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage[toc,page]{appendix}
\usepackage{color}
\definecolor{lightgray}{rgb}{.9,.9,.9}
\definecolor{darkgray}{rgb}{.4,.4,.4}
\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
\floatname{algorithm}{Procedure}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

@@

\usepackage{graphicx}
\usepackage[
n,
operators,
advantage,
sets,
adversary,
landau,
probability,
notions,	
logic,
ff,
mm,
primitives,
events,
complexity,
asymptotics,
keys]{cryptocode}
\usepackage[colorinlistoftodos]{todonotes}

@@

\title{MixEth: efficient, trustless coin mixing service for Ethereum} %TODO Please add

\titlerunning{MixEth: efficient, trustless coin mixing service for Ethereum}%optional, please use if title is longer than one line

\author{István András Seres\footnote{Corresponding author: István András Seres, istvanseres@caesar.elte.hu}}{Eötvös Loránd University, Hungary \and \url{http://istvanseres.web.elte.hu/} }{istvanseres@caesar.elte.hu}{https://orcid.org/0000-0003-0143-4057}{}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty. Please provide at least the name of the affiliation and the country. The full address is optional

\author{Dániel A. Nagy}{Eötvös Loránd University, Hungary}{daniel@ethereum.org}{}{}
\author{Chris Buckland}{King's College London, United Kingdom}{cpbuckland88@gmail.com}{}{is supported by an Ethereum Foundation scaling grant and an Ethereum Community Fund grant.}
\author{Péter Burcsi}{Eötvös Loránd University, Hungary}{bupe@inf.elte.hu}{https://orcid.org/0000-0003-3306-6500}{}

\authorrunning{I.\,A. Seres and D.\,A. Nagy and C. Buckland and P. Burcsi}%TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

\Copyright{István András Seres and Dániel A. Nagy and Chris Buckland and Péter Burcsi}%TODO mandatory, please use full first names. OASIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\ccsdesc{Theory of computation~Cryptographic protocols}
%\ccsdesc[100]{Theory of Computation~Computational complexity and cryptography~Cryptographic protocols}
%\ccsdesc[100]{Cryptographic protocols}%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm

\keywords{Cryptography, Verifiable shuffle, Anonymity, Cryptocurrency, Ethereum, Coin mixer, State Channel}%TODO mandatory; please add comma-separated list of keywords

\category{}%optional, e.g. invited paper

\relatedversion{}%optional, e.g. full version hosted on arXiv, HAL, or other respository/website
%\relatedversion{A full version of the paper is available at \url{...}.}

\supplement{\url{https://github.com/seresistvanandras/MixEth}}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...

\funding{The research at Eötvös Loránd University was partially supported by the European Union, co-financed by the European Social Fund (EFOP-3.6.2-16-2017-00012).}%optional, to capture a funding statement, which applies to all authors. Please enter author specific funding statements as fifth argument of the \author macro.

\acknowledgements{We would like to thank Liam Horne for helping with the state channel implementation, Barry Whitehat, Dmitry Khovratovich and Sina Mahmoodi for the insightful comments and discussions.}%optional

%\nolinenumbers %uncomment to disable line numbering

%\hideOASIcs  %uncomment to remove references to OASIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\EventEditors{John Q. Open and Joan R. Access}
%\EventNoEds{2}
%\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
%\EventShortTitle{CVIT 2016}
%\EventAcronym{CVIT}
%\EventYear{2016}
%\EventDate{December 24--27, 2016}
%\EventLocation{Little Whinging, United Kingdom}
%\EventLogo{}
%\SeriesVolume{42}
%\ArticleNo{23}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{Vincent Danos, Maurice Herlihy, Maria Potop-Butucaru, Julien Prat, and Sara Tucci-Piergiovanni}
\EventNoEds{5}
\EventLongTitle{International Conference on Blockchain Economics, Security and Protocols (Tokenomics 2019)}
\EventShortTitle{Tokenomics 2019}
\EventAcronym{Tokenomics}
\EventYear{2019}
\EventDate{May 6--7, 2019}
\EventLocation{Paris, France}
\EventLogo{}
\SeriesVolume{71}
\ArticleNo{11}

\begin{document}

\maketitle

%TODO mandatory: add short abstract of the document
\begin{abstract}
Coin mixing is a prevalent privacy-enhancing technology for cryptocurrency users. In this paper, we present MixEth, which is a trustless coin mixing service for Turing-complete blockchains. MixEth does not rely on a trusted setup and is more efficient than any proposed trustless coin tumbler. It requires only 3 on-chain transactions at most per user and 1 off-chain message. It achieves strong notions of anonymity and is able to resist denial-of-service attacks. Furthermore the underlying protocol can also be used to efficiently shuffle ballots, ciphertexts in a trustless and decentralized manner. 
\end{abstract}

@@

\subsection{ECDSA with arbitrary generator element}
Elliptic Curve Digital Signature Algorithm (ECDSA) is a key component of MixEth. ECDSA is widely deployed in practice, where in most cases signatures are generated and verified with respect to a fixed generator element of the underlying group \cite{fersch2016provable}. Since all generators are equal from a security point of view, a single generator element is usually fixed in order to promote standardization and assist usability.

@@

\subsection{Security goals} \label{securitygoals}
We are aiming to achieve and prove the same notions of security as the ones defined in \cite{meiklejohn2018mobius}, namely anonymity, availability and theft prevention. These notions of anonymity, availability and theft prevention were introduced in \cite{meiklejohn2018mobius}, which are included in the Appendices for sake of self-containedness.

@@

Hereby we only give intuition for the notions of security, for formal definitions the astute reader is referred to the Appendices.

@@

@@

\subsubsection{Theft prevention} \label{sec:theftprevention}
We would like to ensure that neither coins can be withdrawn twice, nor withdrawn by anyone other but the intended recipient.

@@

\section{Security}
Notions of security are proven in the Appendices.

@@

@@

All MixEth smart contracts were written in the Solidity language, which is currently the dominant language for developing Ethereum smart contracts. All MixEth contracts are available online\footnote{https://github.com/seresistvanandras/MixEth}.

\subsection{Fully on-chain implementation} \label{fullyonchainimpl}
Conceivably mixers would like to minimize off-chain coordination, therefore in our first implementation of the MixEth protocol, we assumed that all transactions will take place on-chain. There is only a single off-chain message from receiver to sender, where receiver delivers their public key to the sender. The rest of the protocol happens entirely on-chain.

On-chain storage is extremely expensive: it requires $\num[group-separator={,}]{20000}$ gas to store a $256$-bit number, however if a particular storage slot is already taken and one wants to overwrite it with a non-zero element then storing only consumes $\num[group-separator={,}]{5000}$ gas. To minimize on-chain storage costs, only the last two list of shuffled public keys are stored in the MixEth contract's permanent storage. Note that storing only the latest list of shuffled public keys would not be enough, since honest receivers could not prove to the contract that their shuffled public key is compromised unless also the last but first list of shuffled keys is also available for the contract to check the Chaum-Pedersen proof against. Such a storage structure implies that after uploading the new list of shuffled public keys, a challenging period should proceed in order to let receivers check the correctness of the shuffle and whether their shuffled public key is stored in the smart contract. Furthermore we also allow senders to shuffle and deposit new public keys at the same time, meaning that only $3$ on-chain transactions (shuffle, withdraw mixed coins and withdraw shuffling deposit) are sufficient to complete the protocol.

A great advantage of the fully on-chain version of MixEth is that it allows dynamic anonymity sets. One could potentially deposit funds to the contract and shuffle public keys and leave funds in the mixing contract for indefinite amount of time. As soon as the anonymity set is large enough a receiver could withdraw their assets. A receiver in a MixEth contract with $N$ senders could withdraw their funds after $N^{'}$ shuffling rounds, where $N^{'}$ is arbitrary.  This dynamic nature of the contract could even lead to a single monolithic MixEth contract instead of having multiple MixEth contracts with significantly fragmented anonymity sets. A single MixEth contract is able to support the mixing of ether and ERC-20 compatible tokens as well. However note that the gas complexity of shuffling transactions grows linearly in the number of participants, therefore the fully on-chain implementation is not capable to support extremely large anonymity sets with participants more than a few hundreds.

@@

Given these adaptations the application proceeds as follows, all participants including senders, shufflers and receivers, deposit funds in a mutli-signature wallet compatible with the Counterfactual framework, they then follow the installation protocols specified by the framework to install the adapted MixEth logic. Afterwards each participant signs a transaction that transfers an equal amount to each withdrawer from the multi-sig, dependent on correct execution of the channelised MixEth application logic. This application logic proceeds as follows: each sender names a public key of a shuffler as in the deposit stage of the on-chain application, then each shuffler takes it in turn to shuffle. After all shuffles have taken place each withdrawer is given a turn to either declare fraud or no-fraud on any shuffle round. Finally each withdrawer then provides proof of ownership by submitting a valid signature on the modified ECDSA scheme. If any of these steps does not occur, or does not occur correctly, the protocol aborts and the conditional transfer does not occur. In this case the perpetrator loses a deposit, either through fraud proof or through failure to take their turn when state is published on-chain. A further modification would be to distribute the slashed deposit to each of the other participants, compensating them for their lost time and the gas costs associated with proving the fault of the other party. Following this protocol the on-chain transactions are now reduced to: one transaction from each participant to deposit funds into the multi-sig, and a set of transactions that send funds from the multi-sig to each of the withdrawers and deposits back to each of the other participants.

@@

\subsection{Minimizing shuffle transactions with trusted execution environments}
One might effectively minimize the number of necessary shuffling rounds to $1$. If a Trusted Execution Environment (TEE), e.g., Intel SGX is used to generate the shuffling transaction, then even a single shuffling transaction would suffice to provide the same level of anonymity as if every participant shuffles the public keys. Any of the participants could upload the TEE-generated shuffling transaction, while the MixEth contract could check that indeed the shuffling transaction was generated by a TEE. Such a shortcut would make our scheme even more practical and efficient, however it would subsume trust in Intel regarding the security and confidentiality of the TEE.
